Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2025-01-17 article.tex
Replace ellipticPlate with spherical cavity and update results

The cell-centred stress $\bb{\sigma}_P$ is calculated as a function of the displacement gradient according to the chosen mechanical law, where the cell-centred displacement gradients are determined using an inverse-distance-weighted first-neighbours least squares method \citep{Jasak1996},

@@

So, this Rhie-Chow stabilisation can be seen to take the form of a \emph{jump} term; that is, it is a function of the jump in solution between neighbouring cells.
The two states, $\bb{u}_P^*$ and $\bb{u}_{N_{f_i}}^*$, are evaluated halfway between $P$ and $N_{f_i}$, and it may not be at a face centre; however, as noted by \citet{Nishikawa2010}, this will not affect the second-order accuracy of the method; consequently, the user is free to choose the value of $\alpha$ for stabilisation purposes.
% but it doesn't matter because this team is only stabilisation and it vanishes in the grid refinement.
%As long as it vanishes for linear functions, second-order accuracy is preserved. It means that the parameter alpha can be chosen solely for the purpose of stabilization.

@@

The manufactured displacement solution is applied at the domain's boundaries (prescribed displacements), and inertial effects are neglected.
Three mesh types are examined:
%(i) hexahedra, (ii) tetrahedra, and (iii) polyhedra (shown in Figure \ref{fig:mms_mesh}).
(i) \emph{regular} tetrahedra, (ii) \emph{regular} polyhedra (shown in Figure \ref{fig:mms_mesh}), (iii) \emph{regular} hexahedra, and (iv) \emph{distorted} hexahedra.
The second coarsest meshes are shown in Appendix \ref{app:meshes}.
The tetrahedral meshes are created using Gmsh \citep{geuzaine2009gmsh}, while the polyhedral meshes are created by converting the tetrahedral meshes to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.
The regular hexahedral meshes are created using the OpenFOAM \texttt{blockMesh} utility, and the distorted hexahedral meshes are created by perturbing the points of the regular hexahedra by a random vector of magnitude less than 0.3 times the local minimum edge length.
%Points on the corners and edges of the cube domain are not moved, while the remaining boundary points are limited to slide along the boundary.
%During perturbation, if needed, the local point perturbation is iteratively reduced to ensure the local distorted cell volumes are not less than 10\% of their original volume and the maximum face non-orthogonality is less than $70^\circ$.
%Consequently, the meshes can be considered moderately distorted.
%Appendix \ref{app:meshes} includes images of all three cell types for both regular and distorted configurations.
Starting from an initial mesh spacing of $0.04$ m, six meshes of each type are created by successively halving the spacing.
The cell numbers for the hexahedral and polyhedral meshes are 125, $1\,000$, $8\,000$, $64\,000$, $512\,000$, and $4\,096\,000$, while the tetrahedral mesh cell counts are 384, $4\,374$, $41\,154$, $355\,914$, $2\,958\,234$, and $24\,118\,074$.
For the same average cell width, the cell counts show that the tetrahedral meshes have more cells by a factor of 3 to 6.
Table \ref{tab:mmsMesh} lists the average and maximum face non-orthogonality for the meshes of different cell types, where face non-orthogonality is defined as the angle made by the vector between the two adjacent cell centres across the common face and the face normal.
\begin{table}[htb]
    \centering
    \begin{tabular}{lll}
        \hline
        Cell type & Average & Maximum \\
        \hline
        Hexahedra & 0 &0  \\
        Tetrahedra & 32.71 & 35.26 \\
        Polyhedra & 30.65 & 38.45 \\
        \hline
    \end{tabular}
%    \begin{tabular}{l|cc|cc}
%        \hline
%        Cell type & \multicolumn{2}{c|}{Regular} & \multicolumn{2}{c}{Distorted} \\
%        & Average & Maximum & Average & Maximum \\
%        \hline
%        Hexahedra & 0 &0 & 13.10 & 52.51 \\
%        Tetrahedra & 32.73 & 35.26 & 34.83 & 69.96 \\
%        Polyhedra & 30.90 & 38.38 & 3 & 4 \\
%        \hline
%    \end{tabular}
    \caption{Average and maximum face non-orthogonality (in $^\circ$) for the meshes of different cell types and sizes}
    \label{tab:mmsMesh}
\end{table}

Figure \ref{fig:mms_disp_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for the three mesh types (hexahedral, tetrahedral and polyhedral), while Figure \ref{fig:mms_disp_accuracy}(b) shows the corresponding order of accuracy plots.
For ease of interpretation, the symbol shapes in the figures have been chosen to correspond to the cell shapes: a square for hexahedra, a triangle for tetrahedra and a pentagon for polyhedra.
The maximum ($L_\infty$) and average ($L_2$) displacement discretisation errors are seen to reduce at an approximately second-order rate for all mesh types, except for the $L_2$ error on the hexahedral meshes, which is approximately 2.3 on the finest grid.
%where, interestingly, the errors are, on average, smaller on the polyhedral meshes.
%The reason for this is unclear but may be due to the stencil of the structured polyhedra being more isotropic and containing close neighbours.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_dispErrors_v2} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_disp_orderOfAccuracy_v2}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement magnitude}
	\label{fig:mms_disp_accuracy}
\end{figure}

The predicted $\sigma_{xx}$ stress distribution for a hexahedral mesh with $512\,000$ cells is shown in Figure \ref{fig:mms_stress}(a).
The corresponding cell-wise $\sigma_{xx}$ error distribution is shown in Figure \ref{fig:mms_stress}(b).
The errors of greatest magnitude ($43$ kPa) occur at the boundaries, corresponding to where the local truncation error is higher. % due to the use of one-sided differencing.
\begin{figure}[htbp]
	\centering
	\subfigure[Predicted $\sigma_{xx}$ stress distribution]
	{
		\label{fig:mms_sxx}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx} 
   	}
	\subfigure[Cell-wise $\sigma_{xx}$ error distribution]
	{
		\label{fig:mms_sxx_diff}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx_diff}  
   	}
	\caption{Manufactured solution cube case: the predicted $\sigma_{xx}$ stress distribution on a cut-plane for the regular hexahedral mesh with $512\,000$ cells (left).}
	\label{fig:mms_stress}
\end{figure}
The discretisation errors in the stress magnitude as a function of cell size are shown in Figure \ref{fig:mms_stress_accuracy}(a), and the order of accuracy in Figure \ref{fig:mms_stress_accuracy}(b).
The order of accuracy for the average ($L_2$) stress error is seen to be approximately 1.5 for the hexahedral and polyhedral meshes.
In contrast, the average stress error order for the tetrahedral meshes is 1.
Similarly, the maximum ($L_\infty$) stress order of accuracy is seen to approach 1 for all three mesh types.
\begin{figure}[htbp]
	\centering
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stressErrors_v2} 
   	}
	\subfigure[Stress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stress_orderOfAccuracy_v2}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for stress magnitude}
	\label{fig:mms_stress_accuracy}
\end{figure}

%\hl{Distorted grids}

\paragraph{Case 1b: Spherical Cavity in an Infinite Solid Subjected to Remote Stress}
This 3-D problem consists of a spherical cavity with radius $a = 0.2$ m (Figure \ref{fig:spherical_cavity}) in an infinite, isotropic linear elastic solid ($E = 200$ GPa, $\nu = 0.3$).
Far from the cavity, the solid is subjected to a tensile stress $\sigma_{zz} = T = 1$ MPa, with all other stress components zero.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.4\textwidth]{figures/spherical_cavity.pdf} 
   \caption{Spherical cavity case geometry, showing the polyhedral mesh with $4\,539$}
   \label{fig:spherical_cavity}
\end{figure}
The analytical expressions for the stress and displacement distributions are given in Appendix \ref{app:sphericalCavity}.

The computational solution domain is taken as one-eighth of a $1 \times 1 \times 1$ m cube aligned with the Cartesian axes, with one corner at the centre of the sphere.
The analytical tractions are applied at the far boundaries of the domain to mitigate the effects of finite geometry.
Unstructured polyhedral meshes are employed with grading towards the cavity.
The cell sizes at the cavity surfaces are 100, 50, 25, 12.5, 6.25, and 3.125 mm, and the corresponding cell counts are 976, $4\,552$ (Figure \ref{fig:spherical_cavity}), $29\,611$, $213\,100$, $\,614\,261$.
Initially, unstructured tetrahedral meshes were generated using the Gmsh meshing utility \cite{geuzaine2009gmsh}, followed by conversion to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.

\hl{The spherical cavity case errors seem to approach zero order accuracy}
\hl{Maybe we have hit the precision limit...?}
\hl{We may leave this case out}

\paragraph{Case 2: Out-of-plane bending of an elliptic plate}
This 3-D, static, linear elastic test case (Figure \ref{fig:elliptic_plate}) consists of a thick elliptic plate (0.6 m thick) with a centred elliptic hole, with the inner and outer ellipses given as
\begin{eqnarray}
	\left(\frac{x}{2}\right)^2 + \left(\frac{y}{1}\right)^2 = 1 & \text{inner ellipse} \\
	\left(\frac{x}{3.25}\right)^2 + \left(\frac{y}{2.75}\right)^2 = 1 & \text{outer ellipse}
\end{eqnarray}
The case has been described by the National Agency for Finite Element Methods and Standards (NAFEMS) \cite{Hitchings1987}, and analysed using finite volume procedures by \citet{Demirdzic1997a} and \citet{Cardiff2016a}.
Symmetry allows one-quarter of the geometry to be simulated.
A constant pressure of 1 MPa is applied to the upper surface, and the outer surface is fully clamped.
The mechanical properties are: $E = 210$ GPa, $\nu = 0.3$.
Six successively refined hexahedral meshes are used, with cell counts of 45, 472 (Figure \ref{fig:elliptic_plate}), $4\,140$, $34\,968$, $287\,280$ and $2\,438\,242$.
\begin{figure}[htbp]
   \centering
%\includegraphics[width=0.5\textwidth]{figures/elliptic_plate.pdf} ellipticPlate-geometry
%	\subfigure[Mesh containing 472 hexahedral cells]
%	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate.pdf} 
%	}
   \caption{Elliptic Plate geometry and mesh containing 472 hexahedral cells}
   \label{fig:elliptic_plate}
\end{figure}

The prediction for the equivalent (von Mises) stress in the domain are shown in Figure \ref{fig:elliptic_plate_sigmaEq}(a), and the values along the line $r = \sqrt{x^2 + y^2} = 2.1$ m, $z = 0.3$ m are shown in Figure \ref{fig:elliptic_plate_sigmaEq}(b).
The results from the finest grid in \citet{Demirdzic1997a} are given for comparison, where good agreement is seen;
the small offset between the finest mesh predictions and those from \citet{Demirdzic1997a} are likely due to errors introduced when extracting the \citet{Demirdzic1997a} results using WebPlotDigitizer \citep{WebPlotDigitizer}.
The sample values have been calculated by generating 40 uniformly spaced angles between 0 and $\nicefrac{\pi}{2}$ along the line, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
\begin{figure}[htbp]
   \centering
   %\includegraphics[width=0.5\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	\subfigure[Equivalent stress distribution for the mesh with $2\,438\,242$ cells. The deformation is scaled by $1\,000$ and a translucent line indicates the outline of the undeformed geometry]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq}  
	}
	\subfigure[Equivalent stress along the line $r = 2.1$, $z = 0.3$ m]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	}
   \caption{Equivalent (von Mises) stress distribution in the elliptic plate}
   \label{fig:elliptic_plate_sigmaEq}
\end{figure}

@@

			\textbf{MMS - regular} & 384 & 0 & $78$ 				& 0 & 79 \\
			\emph{3-D, static,}	& $4\,374$ & 0 & $86$ 			& 0 & 94 \\
			\emph{linear elastic} & $41\,154$ & 1 & $195$  		& 2 & 181 \\
			\hl{cell type}	&  $355\,914$ & 4 & $1\,063$ 		& 9 & $1\,289$ \\
				& $2\,958\,234$ & 41 & $6\,724$ 	& 92 & $6\,174$ \\
				& $24\,118\,074$ & 486 & $30\,606$ & $1\,732$ & $30\,601$ \\

@@

			\textbf{Elliptic} & 45 & 0 & $72$ & 0 & 76 \\
			\textbf{Plate} & 472 & 0 & $78$ & 0 & 81 \\
			\emph{3-D, static,} & $4\,140$ & 1 & $153$ & 8 & 124 \\
			\emph{linear elastic} & $34\,968$ & 7 & $754$ & 149 & 660 \\
				& $287\,280$ & 95 & $3\,943$ & $2\,694$ & $3\,661$ \\
				& $2\,438\,242$ & 988 & $21\,884$ & $45\,692$ & $20\,348$ \\

@@

@@

			\textbf{Membrane ii} & 9 	& 1 & 81 		& 1 & 78 \\
			\emph{2-D, static,} & 36 	& 1& 81 		& 2 & 78 \\
			\emph{hyperelastic} & 144 & 3 & 84 		& 5 & 80 \\
				& 576 			& 9 & 97 		& 26 & 91 \\
				& $2\,304$ 		& 34 & 144 	& 166 & 132  \\
				& $9\,216$ 		& 161 & 256  	& $1\,374$ & 357 \\
				& $36\,864$ 		& 860 & 554  	& $15\,991$ & $1\,053$ \\
				& $147\,456$ 		& $1\,585$ & $2\,847$ & $135\,851$ & $2\,341$ \\

@@

>>>>

The cell-centred stress $\bb{\sigma}_P$ is calculated as a function of the displacement gradient according to the chosen mechanical law, for example, as shown in Appendix \ref{app:mechLaws}.
\hl{magSf in OF}
The presented discretisation is second-order accurate in space for displacement if the cell-centred displacement gradients (and the stress) are at least first-order accurate in space, even if the cell faces are not flat.
To achieve this, the cell-centred displacement gradients are determined using an inverse-distance-weighted first-neighbours least squares method \citep{Jasak1996},

@@

So, this Rhie-Chow stabilisation can be seen to take the form of a \emph{jump} term; that is, it is a function of the jump in solution between neighbouring cells.
The two states, $\bb{u}_P^*$ and $\bb{u}_{N_{f_i}}^*$, are evaluated halfway between $P$ and $N_{f_i}$, and it may not be at a face centre; however, as noted by \citet{Nishikawa2010}, this will not affect the second-order accuracy of the method; consequently, the user is free to choose the value of $\alpha$ for stabilisation and accuracy purposes.
% but it doesn't matter because this team is only stabilisation and it vanishes in the grid refinement.
%As long as it vanishes for linear functions, second-order accuracy is preserved. It means that the parameter alpha can be chosen solely for the purpose of stabilization.

@@

The manufactured displacement solution is applied at the domain's boundaries (prescribed displacements), and inertial effects are neglected.
Three mesh types are examined:
%(i) hexahedra, (ii) tetrahedra, and (iii) polyhedra (shown in Figure \ref{fig:mms_mesh}).
(i) \emph{regular} tetrahedra, (ii) \emph{regular} polyhedra (shown in Figure \ref{fig:mms_mesh}), (iii) \emph{regular} hexahedra, and (iv) \emph{distorted} hexahedra.
The second coarsest meshes are shown in Appendix \ref{app:meshes}.
The tetrahedral meshes are created using Gmsh \citep{geuzaine2009gmsh}, while the polyhedral meshes are created by converting the tetrahedral meshes to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.
The regular hexahedral meshes are created using the OpenFOAM \texttt{blockMesh} utility, and the distorted hexahedral meshes are created by perturbing the points of the regular hexahedra by a random vector of magnitude less than 0.3 times the local minimum edge length.
%Points on the corners and edges of the cube domain are not moved, while the remaining boundary points are limited to slide along the boundary.
%During perturbation, if needed, the local point perturbation is iteratively reduced to ensure the local distorted cell volumes are not less than 10\% of their original volume and the maximum face non-orthogonality is less than $70^\circ$.
%Consequently, the meshes can be considered moderately distorted.
%Appendix \ref{app:meshes} includes images of all three cell types for both regular and distorted configurations.
Starting from an initial mesh spacing of $0.04$ m, six meshes of each type are created by successively halving the spacing.
The cell numbers for the hexahedral and polyhedral meshes are 125, $1\,000$, $8\,000$, $64\,000$, $512\,000$, and $4\,096\,000$, while the tetrahedral mesh cell counts are 384, $4\,374$, $41\,154$, $355\,914$, $2\,958\,234$, and $24\,118\,074$.
For the same average cell width, the cell counts show that the tetrahedral meshes have more cells by a factor of 3 to 6.
%Table \ref{tab:mmsMesh} lists the average and maximum face non-orthogonality for the meshes of different cell types, where face non-orthogonality is defined as the angle made by the vector between the two adjacent cell centres across the common face and the face normal.
%\begin{table}[htb]
%    \centering
%    \begin{tabular}{lll}
%        \hline
%        Cell type & Average & Maximum \\
%        \hline
%        Hexahedra & 0 &0  \\
%        Tetrahedra & 32.71 & 35.26 \\
%        Polyhedra & 30.65 & 38.45 \\
%        \hline
%    \end{tabular}
%    \begin{tabular}{l|cc|cc}
%        \hline
%        Cell type & \multicolumn{2}{c|}{Regular} & \multicolumn{2}{c}{Distorted} \\
%        & Average & Maximum & Average & Maximum \\
%        \hline
%        Hexahedra & 0 &0 & 13.10 & 52.51 \\
%        Tetrahedra & 32.73 & 35.26 & 34.83 & 69.96 \\
%        Polyhedra & 30.90 & 38.38 & 3 & 4 \\
%        \hline
%    \end{tabular}
%    \caption{Average and maximum face non-orthogonality (in $^\circ$) for the meshes of different cell types and sizes}
%    \label{tab:mmsMesh}
%\end{table}

Figure \ref{fig:mms_disp_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for the four mesh types (tetrahedral, polyhedral, regular and distorted hexahedral), while Figure \ref{fig:mms_disp_accuracy}(b) shows the corresponding order of accuracy plots.
For ease of interpretation, the symbol shapes in the figures have been chosen to correspond to the cell shapes: a triangle for tetrahedra, a pentagon for polyhedra, a square for regular hexahedra, and a diamond for distorted hexahedra.
The maximum ($L_\infty$) and average ($L_2$) displacement discretisation errors are seen to reduce at an approximately second-order rate for all mesh types, except for the $L_2$ error on the hexahedral meshes, which is approximately 2.3 on the finest grid.
The distorted hexahedral meshes show the largest average and maximum errors but still approach second-order accuracy as the element spacing decreases.
%where, interestingly, the errors are, on average, smaller on the polyhedral meshes.
%The reason for this is unclear but may be due to the stencil of the structured polyhedra being more isotropic and containing close neighbours.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_dispErrors_v2} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_disp_orderOfAccuracy_v2}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement magnitude}
	\label{fig:mms_disp_accuracy}
\end{figure}

The predicted $\sigma_{xx}$ stress distribution for a hexahedral mesh with $512\,000$ cells is shown in Figure \ref{fig:mms_stress}(a).
The corresponding cell-wise $\sigma_{xx}$ error distribution is shown in Figure \ref{fig:mms_stress}(b).
The errors of greatest magnitude ($43$ kPa) occur at the boundaries, corresponding to where the local truncation error is higher. % due to the use of one-sided differencing.
\begin{figure}[htbp]
	\centering
	\subfigure[Predicted $\sigma_{xx}$ stress distribution]
	{
		\label{fig:mms_sxx}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx} 
   	}
	\subfigure[Cell-wise $\sigma_{xx}$ error distribution]
	{
		\label{fig:mms_sxx_diff}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx_diff}  
   	}
	\caption{Manufactured solution cube case: the predicted $\sigma_{xx}$ stress distribution on a cut-plane for the regular hexahedral mesh with $512\,000$ cells (left).}
	\label{fig:mms_stress}
\end{figure}
The discretisation errors in the stress magnitude as a function of cell size are shown in Figure \ref{fig:mms_stress_accuracy}(a), and the order of accuracy in Figure \ref{fig:mms_stress_accuracy}(b).
The order of accuracy for the average ($L_2$) stress error is seen to be approximately 1.5 for the hexahedral and polyhedral meshes.
In contrast, the average stress error order for the tetrahedral and distorted hexahedral meshes is 1.
Similarly, the maximum ($L_\infty$) stress order of accuracy is seen to approach 1 for all mesh types.
Unlike for the displacements, the greatest stress errors are seen in the tetrahedral rather than the distorted hexahedral meshes; however, the greatest stress maximum errors occur in the distorted hexahedral meshes.
\begin{figure}[htbp]
	\centering
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stressErrors_v2} 
   	}
	\subfigure[Stress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stress_orderOfAccuracy_v2}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for stress magnitude}
	\label{fig:mms_stress_accuracy}
\end{figure}

The presented results agree with the theory: the least squares gradient scheme should be at least first-order accurate for random grids, with greater than first-order accuracy on regular grids due to local truncation error cancellations.
In addition, the displacement predictions should be at least second-order accurate on all grid types as long as the gradient scheme achieves at least first-order accuracy.

\paragraph{Case 2: Spherical Cavity in an Infinite Solid Subjected to Remote Stress}
This classic 3-D problem consists of a spherical cavity with radius $a = 0.2$ m (Figure \ref{fig:spherical_cavity}) in an infinite, isotropic linear elastic solid ($E = 200$ GPa, $\nu = 0.3$).
Far from the cavity, the solid is subjected to a tensile stress $\sigma_{zz} = T = 1$ MPa, with all other stress components zero.
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.4\textwidth]{figures/spherical_cavity} 
	\subfigure[Polyhedral mesh with $4\,539$]
	{
	   \includegraphics[height=0.4\textwidth]{figures/spherical_cavity} 
   	}
	\subfigure[Axial ($zz$) stress distribution on the mesh with $1\,614\,261$ cells]
	{
	   \includegraphics[height=0.4\textwidth]{figures/spherical_cavity_axial_stress} 
	   \label{fig:spherical_cavity_stress}
   	}
   \caption{Spherical cavity case}
   \label{fig:spherical_cavity}
\end{figure}
The analytical expressions for the stress, derived by \citet{Southwell1926},  and displacement, derived by \citet{Goodier1933}, are given in Appendix \ref{app:sphericalCavity}.
The problem is characterised by localised by a stress concentration near the cavity on the plane perpendicular to the loading, which drops off rapidly away from the cavity.

The computational solution domain is taken as one-eighth of a $1 \times 1 \times 1$ m cube aligned with the Cartesian axes, with one corner at the centre of the sphere.
The problem is axisymmetric but is analysed here using a 3-D domain to allow a graded unstructured polyhedral mesh to be assessed.
The analytical tractions are applied at the far boundaries of the domain to mitigate the effects of finite geometry.
%Unstructured polyhedral meshes are employed with grading towards the cavity.
The cell sizes at the cavity surfaces are 100, 50, 25, 12.5, 6.25, and 3.125 mm, and the corresponding cell counts are 976, $4\,552$ (Figure \ref{fig:spherical_cavity}), $29\,611$, $213\,100$, $1\,614\,261$.
Initially, unstructured tetrahedral meshes were generated using the Gmsh meshing utility \cite{geuzaine2009gmsh}, followed by conversion to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.

Figure \ref{fig:spherical_cavity_stress} shows the predicted axial ($zz$) stress field on the mesh with $1\,614\,261$ cells.
The predicted mean ($L_2$) and maximum ($L_\infty$) displacement and axial stress discretisation errors as a function of the average cell width are presented in Figure \ref{fig:spherical_cavity_accuracy}.
The mean and maximum displacement errors are seen to reduce at an approximately second-order rate, while the stress errors are seen to reduce at a first-order rate.
As seen in the previous case, the results agree with the theoretical expectations for unstructured (irregular) meshes.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
	   \includegraphics[width=0.45\textwidth]{figures/sphericalCavityDispError.pdf} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
	   \includegraphics[width=0.45\textwidth]{figures/sphericalCavityDispOrder.pdf} 
   	}
	\subfigure[Axial ($zz$) stress discretisation errors]
	{
	   \includegraphics[width=0.45\textwidth]{figures/sphericalCavityStressError.pdf} 
   	}
	\subfigure[Axial ($zz$) stress discretisation error order of accuracy]
	{
	   \includegraphics[width=0.45\textwidth]{figures/sphericalCavityStressOrder.pdf} 
   	}
	\caption{Spherical cavity discretisation errors as a function of the average cell spacing}
	\label{fig:spherical_cavity_accuracy}
\end{figure}

%The predicted $\sigma_{xx}$ stress distribution for a hexahedral mesh with $512\,000$ cells is shown in Figure \ref{fig:mms_stress}(a).
%The corresponding cell-wise $\sigma_{xx}$ error distribution is shown in Figure \ref{fig:mms_stress}(b).
%The errors of greatest magnitude ($43$ kPa) occur at the boundaries, corresponding to where the local truncation error is higher. % due to the use of one-sided differencing.
%\begin{figure}[htbp]
%	\centering
%	\subfigure[Predicted $\sigma_{xx}$ stress distribution]
%	{
%		\label{fig:mms_sxx}
%   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx} 
%   	}
%	\subfigure[Cell-wise $\sigma_{xx}$ error distribution]
%	{
%		\label{fig:mms_sxx_diff}
%   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx_diff}  
%   	}
%	\caption{Manufactured solution cube case: the predicted $\sigma_{xx}$ stress distribution on a cut-plane for the regular hexahedral mesh with $512\,000$ cells (left).}
%	\label{fig:mms_stress}
%\end{figure}

%\paragraph{Case 2: Out-of-plane bending of an elliptic plate}
%This 3-D, static, linear elastic test case (Figure \ref{fig:elliptic_plate}) consists of a thick elliptic plate (0.6 m thick) with a centred elliptic hole, with the inner and outer ellipses given as
%\begin{eqnarray}
%	\left(\frac{x}{2}\right)^2 + \left(\frac{y}{1}\right)^2 = 1 & \text{inner ellipse} \\
%	\left(\frac{x}{3.25}\right)^2 + \left(\frac{y}{2.75}\right)^2 = 1 & \text{outer ellipse}
%\end{eqnarray}
%The case has been described by the National Agency for Finite Element Methods and Standards (NAFEMS) \cite{Hitchings1987}, and analysed using finite volume procedures by \citet{Demirdzic1997a} and \citet{Cardiff2016a}.
%Symmetry allows one-quarter of the geometry to be simulated.
%A constant pressure of 1 MPa is applied to the upper surface, and the outer surface is fully clamped.
%The mechanical properties are: $E = 210$ GPa, $\nu = 0.3$.
%Six successively refined hexahedral meshes are used, with cell counts of 45, 472 (Figure \ref{fig:elliptic_plate}), $4\,140$, $34\,968$, $287\,280$ and $2\,438\,242$.
%\begin{figure}[htbp]
%   \centering
%%\includegraphics[width=0.5\textwidth]{figures/elliptic_plate.pdf} ellipticPlate-geometry
%%	\subfigure[Mesh containing 472 hexahedral cells]
%%	{
%		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate.pdf} 
%%	}
%   \caption{Elliptic Plate geometry and mesh containing 472 hexahedral cells}
%   \label{fig:elliptic_plate}
%\end{figure}
%
%The prediction for the equivalent (von Mises) stress in the domain are shown in Figure \ref{fig:elliptic_plate_sigmaEq}(a), and the values along the line $r = \sqrt{x^2 + y^2} = 2.1$ m, $z = 0.3$ m are shown in Figure \ref{fig:elliptic_plate_sigmaEq}(b).
%The results from the finest grid in \citet{Demirdzic1997a} are given for comparison, where good agreement is seen;
%the small offset between the finest mesh predictions and those from \citet{Demirdzic1997a} are likely due to errors introduced when extracting the \citet{Demirdzic1997a} results using WebPlotDigitizer \citep{WebPlotDigitizer}.
%The sample values have been calculated by generating 40 uniformly spaced angles between 0 and $\nicefrac{\pi}{2}$ along the line, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
%\begin{figure}[htbp]
%   \centering
%   %\includegraphics[width=0.5\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
%	\subfigure[Equivalent stress distribution for the mesh with $2\,438\,242$ cells. The deformation is scaled by $1\,000$ and a translucent line indicates the outline of the undeformed geometry]
%	{
%		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq}  
%	}
%	\subfigure[Equivalent stress along the line $r = 2.1$, $z = 0.3$ m]
%	{
%		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
%	}
%   \caption{Equivalent (von Mises) stress distribution in the elliptic plate}
%   \label{fig:elliptic_plate_sigmaEq}
%\end{figure}
%
%

@@

			\textbf{MMS}			& 125 		& 0 & $79$ 				& 0 & 79 \\
			\emph{regular hex}		& $1\,000$ 	& 0 & $92$ 			& 0 & 94 \\
			\emph{3-D, static,} 		& $8\,00$ 		& 1 & $197$  		& 2 & 181 \\
			\emph{linear elastic}		&  $64\,000$ 	& 4 & $1\,211$ 		& 9 & $1\,289$ \\
								& $512\,000$ 	& 44 & $5\,961$ 	& 92 & $6\,174$ \\
								& $4\,096\,000$ & 517 & $23\,264$ & $1\,732$ & $30\,601$ \\

@@

			\textbf{Spherical}	& 976			& 0 & $92$			& 0 & 93 \\
			\textbf{Cavity}		&  $4\,552$		& 0 & $179$			& 4 & 167 \\
			\emph{3-D, static,} 	&  $29\,611$		& 5 & $926$			& 49 & $1\,098$ \\
			\emph{linear elastic} 	& $213\,100$		& 71 & $5\,794$		& x & x \\
							& $1\,614\,261$ 	& $1\,060$ & $23\,455$ 	& $x\,xxx$ & $x\,x$ \\

@@

%			\textbf{Elliptic} & 45 & 0 & $72$ & 0 & 76 \\
%			\textbf{Plate} & 472 & 0 & $78$ & 0 & 81 \\
%			\emph{3-D, static,} & $4\,140$ & 1 & $153$ & 8 & 124 \\
%			\emph{linear elastic} & $34\,968$ & 7 & $754$ & 149 & 660 \\
%				& $287\,280$ & 95 & $3\,943$ & $2\,694$ & $3\,661$ \\
%				& $2\,438\,242$ & 988 & $21\,884$ & $45\,692$ & $20\,348$ \\

@@

			\textbf{Membrane ii} 	& 9 				& 0 & 77 		& 1 & 78 \\
			\emph{2-D, static,} 	& 36 				& 0 & 77 		& 2 & 78 \\
			\emph{hyperelastic} 	& 144 			& 0 & 78 		& 5 & 80 \\
							& 576 			& 0 & 85 		& 26 & 91 \\
							& $2\,304$ 		& 1 & 108 		& 166 & 132  \\
							& $9\,216$ 		& 2 & 186  	& $1\,374$ & 357 \\
							& $36\,864$ 		& 10 & 517  	& $15\,991$ & $1\,053$ \\
							& $147\,456$ 		& 44 & $1\,911$ & $135\,851$ & $2\,341$ \\

@@

\hl{Seg vs snes-seg}
